Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Even more focused Abstract

\begin{abstract}
We observed that several widely used Haskell libraries do not have
tests.
Test code assists developers in maintaining correctness when extending
software, and shows users how an API is supposed to be used.
To ease the production and enhance the value of test code, we advocate
behavior driven development with two tools:
Doctest integrated with QuickCheck for user documentation and
Hspec with new mnemonic combinators for code documentation.
Our approach can be used for design, documentation and automated
testing.  We hope that this motivates Haskell programmers to write
more and better tests.

>>>>

\begin{abstract}
We observed that several widely used Haskell libraries do not have
tests.
Test code assists developers in maintaining correctness when extending
software, and shows users how an API is supposed to be used.
To ease the production and enhance the value of test code, we advocate
behavior driven development with two tools:
Doctest for user documentation and
Hspec for code documentation.
Our approach can be used for design, documentation and automated
testing.  We hope that this motivates Haskell programmers to write
more and better tests.
